Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

\subsection{Proof of Theorem~\ref{thm:main-recur}} \label{sec:ksj:thm1}

As stated in Theorem~\ref{thm:main-recur}, we are given an algorithm $\A$ that can solve any $(k-1)$-SJ problem in $F_{k-1}(n, \out)$ time, where $n$ and $\out$ are the input and output sizes, respectively. Equipped with $\A$, we will show how to find the result tuples of each category within the time complexity of \eqref{eqn:main:reccurrence}.

@@

>>>>

The rest of this section serves as a proof of Theorem~\ref{thm:main-recur}. Theorem~\ref{thm:main-alg} is a corollary of Theorem~\ref{thm:main-recur}, as we show in Appendix~\ref{app:main-alg}. As stated in Theorem~\ref{thm:main-recur}, we are given an algorithm $\A$ that can solve any $(k-1)$-SJ problem in $F_{k-1}(n, \out)$ time, where $n$ and $\out$ are the input and output sizes, respectively. Equipped with $\A$, we will show how to find the result tuples of each category within the time complexity of \eqref{eqn:main:reccurrence}.

@@

\section{Proof of Theorem~\ref{thm:main-alg}} \label{app:main-alg}
